Fingerprinting \titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}

### 2018-11-08 paper.tex
Add categories and subject descriptors

% A category with the (minimum) three required fields
\category{H.4}{Security Systems Applications}{Miscellaneous}
%A category including the fourth, optional field follows...
\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

>>>>

% A category with the (minimum) three required fields
\category{C.2.0}{Computer-Communication Networks}{General}---\textit{Security and Protection}
%A category including the fourth, optional field follows...
\category{D.4.6}{Operating Systems}{Security and Protection}---\textit{Authentication}
\category{K.6.5}{Management of Computing and Information Systems}{Security and Protection}---\textit{Authentication}
